Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
lhs correction to keep only low and fail

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(rhs,"fail"))
```

@@

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(rhs,"low"))
```

>>>>

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(lhs,"fail"), 
         str_detect(rhs,"fail"))
```

@@

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(lhs,"low"), 
         str_detect(rhs,"low"))
```
